Long-term visual SLAM in industrial environments faces a bottleneck that neither geometric SLAM nor object-level semantic mapping directly addresses: which detected objects deserve durable map slots, and which should be rejected as transient or dynamic contamination? Open-vocabulary detection pipelines produce candidate object instances from every frame, but naively inserting all geometrically consistent detections contaminates the map with forklifts, carts, and single-visit phantoms---a dynamic contamination problem recognized in dynamic SLAM literature~\cite{bescos2018dynaslam} but not resolved at the semantic map-admission level. This paper formulates \textbf{session-level map admission control} as a distinct contribution: an explicit object-maintenance layer between perception and the map that transforms open-vocabulary RGB-D segmentation outputs into observation, tracklet, map-object, and revision layers, then applies boolean criteria (multi-session presence, minimum observation support, label consistency, static dominance) to admit stable semantic landmarks and reject dynamic contamination. We evaluate the framework on the TorWIC dataset~\cite{barath2023povslam}, reporting a reproducible evidence ladder across same-day (203 observations / 11 candidate clusters $\rightarrow$ 5 retained), cross-day (240/10$\rightarrow$5), and cross-month (297/14$\rightarrow$7) Aisle protocols, with a separate Hallway within-site variation branch (537/16$\rightarrow$9). Forklift-like evidence is consistently rejected as dynamic contamination (50.0\%--71.4\% rejection share across all four protocols). We validate the admission policy through parameter ablation across 27 combinations, showing that min\_sessions and min\_frames are sensitive filters while max\_dynamic\_ratio is naturally saturated by data bimodality (infrastructure at dynamic ratio~0.00, forklifts at~$\geq$0.83). Baseline comparison against naive-all-admit and purity/support-heuristic strategies demonstrates that simpler heuristics cannot reject forklifts (phantom risk~20.0\%$\rightarrow$0.0\% with the full policy, McNemar $p{<}0.001$), while per-category retention analysis confirms forklift rejection is universal and infrastructure retention is selective but interpretable. A 16-configuration DROID-SLAM trajectory analysis reveals that selective low-coverage semantic masks are trajectory-neutral ($|\Delta\text{APE}| \leq 0.006$~mm, 11/16 configs across 5 sessions and Aisle/Hallway within-site variation), while aggressive mask strategies introduce measurable perturbations ($0.92$--$7.52$~mm). The contribution is bounded: not a lifelong SLAM benchmark, not dense dynamic reconstruction, and not a downstream navigation-gain claim---it is an evidence-backed session-level map admission control methodology with per-object provenance at every layer.
